Towards One-Step, Three-Factor \\ Authentication with EarEEG

### 2017-09-19 paper.tex
Submitted version

"One-step two-factor authentication" has been proposed as a new approach
to authentication that can provide the security benefits of two-factor authentication without incurring the hassle cost of two-step verification.
In this study we undertake, to the best of our knowledge, the first
ever study of one-step, three-factor authentication. In computer security,
authenticators are classified into three types: knowledge factors (e.g., passwords
and PINs), possession factors (e.g., physical tokens, ATM cards), and inherence
factors (e.g., fingerprints and other biometrics). By taking advantage of a physical token 
in the form of personalized earpieces, the uniqueness of an individual's brainwaves, and
a choice of mental task to use as one's "passthought", we seek to achieve all three factors 
of authentication in a single step by the user.

Furthermore, the form factor of an earpiece carries significantly less stigama versus scalp-based passthoughts systems. Technology worn in the ear is already an acceptable practice, for example earphones or bluetooth headsets.

We find that we can achieve very low false acceptance rates (FAR) and false rejection rates (FRR) with a single, 
three-electrode earpiece. Interestingly, we found that performance improves in the ear compared to a single electrode on the scalp, a site typically used for collecting EEG data. Additionally, we find that passthoughts could not be spoofed by imposters, even when the imposters had the user's earpiece and knew their chosen passthoughts. Finally we discuss interesting patterns in our promising results, and future work to investigate the robustness of passthoughts in day-to-day life.

@@

The concept of in-ear EEG was introduced in 2011 with a demonstration of the feasibility of recording brainwave signals from within the ear canal \cite{Looney2011}. The in-ear placement can produce signal-to-noise ratios comparable to those from conventional EEG electrode placements, is robust to common sources of artifacts, and can be used in a brain-computer interface (BCI) system based on auditory and visual evoked potentials \cite{Kidmose2013a}. One study attempted to demonstrate user authentication using in-ear EEG, but was only able to attain an accuracy level of 80\%, limited by their use of a consumer-grade device with a single-electrode generic fit earpiece \cite{curran2016passthoughts}. Our study improves on these results by incorporating a physical token (a possession factor) in the form of custom-fitted earpieces with three electrodes each vs. the single channel used in previous work. Additionally we use the OpenBCI system which allows us to capture raw data (the device used in previous work used an unknown proprietary algorithm), simultaneously record from the scalp for validation, and report impedance measures important to data quality assessment and authentication.

@@

When proposing or evaluating authentication paradigms robustness against imposters is often the first consideration, but the usability of these systems is of equal importance as they must conform to a person's needs and lifestyle to warrant adoption and prolonged use. The authors of \cite{sasse2001} describe usability issues with knowledge-based systems like alphanumeric passwords, in particular that it should not be the burden of the user to remember complex passwords that have to be frequently changed. \cite{braz2006} analyzed some of the complexities applying interface human factors heuristics to authentication, and indicate the importance of social acceptibility, learnability, and simplicity of authentication methods. Technology worn on the head faces particular usability issues; in their analysis of user perceptions of such devices, \cite{Genaro2014} identified design, usability, ease of use, and obtrusiveness among the top 10 concerns of users online postings, and qualitatively comments around comfort and "looking weird".

In the proposed system we seek to incorporate the perspectives of this research. Passthoughts such as a favorite song or relaxed breathing are easy for a user to remember and perform, and the choice of an earpiece form factor of our system seeks to address wearability and social perception concerns.

@@

\begin{figure}[t]
\centering
\includegraphics[width=.75\linewidth]{./figures/CFEEEG_piecefig_Right.jpg}
\caption{Labeled photo of one of our manufactured custom-fit earpieces with 3 embedded electrodes located in the concha, front-facing (anterior) in the ear canal, and back-facing (posterior) in the ear canal.}
\label{fig:earpiece_diagram}
\end{figure}

To produce custom ear impressions we first cleaned subjects' ears and injected silicon into the ear canals. A cotton ball with a string attached was placed into the ear canal first. When the silicon dried after a few minutes, the string was pulled to remove the impression from the ear canal. This impression was then scanned with a 3D scanner and the resulting scan modified based on some heuristics to achieve a comfortable fit and to ensure the intended electrode sites will make good contact with the skin. Channels were created in the 3D model to allow wire leads and associated EEG electrodes as well as a plastic tube to deliver audio. This 3D model was then sent to a 3D printer after which wires, leads, and associated AgCl electrodes were installed. The positions of the earpiece electrodes were simplified from those described in \cite{Mikkelsen2015}. We reduced the number of canal electrodes in order to prevent electrical bridging and positioned them approximately 180 degrees apart in the canal (posterior/back and anterior/front locations in the canal). One other electrode was placed in the concha. An example of one of the manufactured earpieces is shown in Figure \ref{fig:earpiece_diagram}.

@@

We used a set of mental tasks based on findings in related work regarding the relative strengths of different tasks in authentication accuracy and usability as reported by participants. \cite{Chuang2013b, curran2016passthoughts} Furthermore, given the in-ear placement of the electrodes and therefore the proximity to the temporal lobes containing the auditory cortex, we tested several novel authentication tasks based specifically on aural imagery or stimuli. The nine authentication tasks and their attributes are listed in Table \ref{tab:tasks}. Our strategy was to select tasks that captured a diversity across dimensions of external stimuli, involving a personal secret, eyes open or closed (due to known effects on EEG), and different types of mental imagery.

@@

\textbf{Task} & \textbf{Description} & \textbf{Stimuli}? & \textbf{Secret}? & \textbf{Eyes} & \textbf{Imagery}\\
\hline
Breathe & Relaxed breathing with eyes closed & No & No & Closed & None\\
Breathe - Open & Relaxed breathing with eyes open & No & No & Open & None\\
Sport & Imagine attempting a chosen physical activity & No & Yes & Closed & Motor\\
Song & Imagine hearing a song & No & Yes & Closed & Aural\\
Song - Open & Song task, with eyes open & No & Yes & Open & Aural\\
Speech & Imagine a chosen spoken phrase & No & Yes & Closed & Aural\\
Listen & Listen to noise modulated at 40 Hz & Yes & No & Closed & None\\
Face & Imagine a chosen person's face & No & Yes & Closed & Visual\\
Sequence & Imagine a chosen face, number, and word on timed cues & Yes & Yes & Open & Visual\\
\hline
\end{tabularx}
\caption{Authentication tasks and their properties. We selected tasks with a variety of different properties, but preferred tasks that did not require external stimuli, as the need to present such stimuli at authentication time could present challenges for usability and user security.}
\label{tab:tasks}%
\end{table*}

\subsection{Data Collection Protocol}
%\label{sec:org2041857}
All sites were cleaned with ethanol prior to electrode placement and a small amount of conductive gel was used on each electrode. For EEG recording we used an 8-channel OpenBCI system \cite{michalska2009openbci} which is open-source and costs about 600 USD; an alternative to medical-grade EEG systems (\textgreater20,000 USD), with demonstrated effectiveness \cite{Frey2016}. The ground was placed at the center of the forehead, approximately AFz according to the 10-20 International Standard for Electrode Placement (ISEP), and reference on the left mastoid. The AFz ground location was intentional to not bias left or right ear recordings, though future systems using one ear only should test relocating the ground to a site on one ear (e.g. the earlobe). six channels were used for the three electrodes on each earpiece (shown in Figure \ref{fig:earpiece_diagram}); for the remaining two channels one AgCl ring electrode was placed on the right mastoid for later re-referencing, and one at approximately Fp1 (ISEP location above the left eye) to validate the data collected in the ears against a common scalp-based placement. Before beginning the experiment, the data from each channel was visually inspected using the OpenBCI interface. Audio stimuli were delivered through small tubes in the earpieces.

During the experiment, participants were seated in a comfortable position in a quiet room facing a laptop on which the instructions and stimuli were presented using PsychoPy \cite{peirce2007psychopy}. All tasks were performed for five trials each, followed by another set of five trials each to reduce boredom and repetition effects. Each trial was 10 seconds in length, for a total of 10 trials or 100 seconds of data collected per task. The instructions were read aloud to the participant by the experimenter, and the participant advanced using a pointer held in their lap to minimize motion artifacts in the data. The experimenter also recorded the participant's chosen secrets for the \textit{sport}, \textit{song}, \textit{face}, \textit{speech}, and \textit{sequence} tasks and reminded the participant of these for the second set of trials. After EEG data collection, participants completed a usability questionnaire.

@@

It is important that the electrical impedances achieved for electrodes are low ($<$10 kOhm) to obtain quality EEG signals. Table \ref{tab:impedances} below summarizes the impedances across the seven participants' six ear channels. With the exception of a few channels in select participants, impedances achieved were good overall. Most of the recorded impedances of the earpiece electrodes were less than 5 k\(\Omega\), a benchmark used widely in previous ear EEG work, and all except two were less than 10 k\(\Omega\). Nonetheless, the data from all electrodes were tested in the remaining two data quality tests.

@@

Since past work has shown that classification tasks in EEG-based brain-computer interfaces (BCI) are linear \ref{Garrett2003a}, we used XGBoost, a popular tool for logistic linear classification \ref{Chen2016}, to analyze the mental task EEG data. Compared to other linear classifiers, XGBoost uses gradient boosting in which an algorithm generates aa decision tree of weak linear classifiers that minimizes a given loss function. Gradient boosting generally improves linear classification results without manually tuning hyperparameters.

@@

For the predictions, the evaluation regards the instances with prediction value larger than 0.5 as positive instances, and the others as negative instances. After updating classifier parameters, the classifier was tested on the withheld validation set. Since negative examples far outweigh positive examples in this dataset, XGBoost atuomatically optimized using the ”error” hyperparameter. Over a set of \(E\) examples containing \(E_W\) wrong examples \(E_W\subset{E}\), XGBoost’s binary classification error rate \(\epsilon\) is calculated as

@@

To further test the robustness of the system, we also conducted a ”leave one out” process for the best performing tasks in which each participant’s FAR was calculated once leaving out every other participant (e.g. CV for P1 with P2 left out, then CV for P1 with P3 left out, etc. for every participant combination).

@@

Our results indicate acceptable accuracy using data from the left ear alone. This corresponds to a desirable scenario, in which the device could be worn like an single earbud. As such, we focus on results from only the left ear in remaining analyses.

@@

FAR and FRR results by task are shown in Figure \ref{fig:meanByTask}, averaged across participants. Across all tasks, the sport task produced the lowest FAR. Specifically, it produced 0.0\% FAR for all seven participants, with a corresponding 1.8\% FRR. This suggests that the authentication scheme can work very well even if we limit the passthoughts to just a single task category, where the users could choose a personalized secret for that task.Interestingly, tasks like \textit{breathe} and \textit{breathe - open} performed very well despite lacking a personalized secret, indicating that even when the task may be the same across participants our classifier was still able to distinguish between them.

@@

In addition to the scales and rankings, we included a few open response questions to ascertain attitudes around use cases for in-ear EEG and passthoughts, and the comfort of wearing an in-ear EEG device in everyday life. Participants first read the prompt, "Imagine a commercially available wireless earbud product is now available based on this technology that you've just experienced. It requires minimal effort for you to put on and wear.", and were asked about use cases for in-ear EEG and passthoughts. Responses about in-ear EEG expectedly included authentication for unlocking a phone or computer and building access, but also aspects of self-improvement such as P4's response "Help people increase focus and productivity". P5 and P6 also indicated a use for measuring engagement with media like movies and music, and relatedly P4 wrote "music playback optimized for current mental state and feelings". In terms of comfort wearing such a device, participants generally responded they would be comfortable, though P5 and P6 stipulated only when they already would be wearing something in the ears like earphones. Notably, three participants also added that imaginging a face was difficult and were concerned about their ability to repeat tasks in the same exact way each time.

A final component of usability we acquired was the ability of the participants to recall their specific chosen passthoughts. Participants were contacted via e-mail approximately two weeks after data collection and asked to reply with the passthoughts they chose for the \textit{song}, \textit{sport}, \textit{speech}, \textit{face}, and \textit{sequence} tasks. All participants correctly recalled all chosen passthoughts, with the exception of one participant who did not recall their chosen word for the \textit{sequence} task.

@@

The real-world implications of this study are limited by the small, relatively homogeneous sample of participants. In the case of this initial evaluation however, the homogeneity of our participant pool strengthens the reported results given that system is meant to distinguish between individuals. In order to establish the validity of this system for widespread real-world use we feel it is necessary to expand the size and diversity of participants in future studies. This sample size is comparable to that of other EEG passthoughts work \cite{Ashby2011, Marcel2007a, Poulos2002, Chuang2013b, curran2016passthoughts} and other custom-fit in-ear EEG research \cite{Kidmose2013a, Mikkelsen2015}. The fitting and manufacturing of custom-fit earpieces was the main limitation to increasing our sample size. This may very well pose a limitation in proliferation and adoption of such a technology as well, although recently there have been developments in at-home kits for creating one's own custom-fitted earpieces \cite{voix2015settable} that could help overcome this barrier.

>>>>

"One-step two-factor authentication" has been proposed as a new approach
to authentication that can provide the security benefits of two-factor authentication without incurring the hassle cost of two-step verification.
In this work we undertake, to the best of our knowledge, the first
ever study and implementation of one-step, \textit{three}-factor authentication. In computer security, authenticators are classified into three types: knowledge factors (e.g., passwords
and PINs), possession factors (e.g., physical tokens, ATM cards), and inherence
factors (e.g., fingerprints and other biometrics). By taking advantage of a physical token 
in the form of personalized earpieces, the uniqueness of an individual's brainwaves, and
a choice of mental task to use as one's "passthought", we seek to achieve all three factors 
of authentication in a single step by the user.

Furthermore, the form factor of an earpiece combats the flaw of the conspicuous and obtrusive nature of traditional EEG systems worn on the scalp. Technology worn in the ear is already a socially accepted practice in many cultures, with examples like earphones or bluetooth headsets.

We find that we can achieve very low false acceptance rates (FAR) and false rejection rates (FRR) with a single, three-electrode earpiece. Interestingly, we found that performance improves in the ear compared to a single electrode on forehead above the left eye, a site typically used for collecting EEG data. Additionally, we find that passthoughts could not be spoofed by imposters, even when the imposters had the user's earpiece and knew their chosen passthoughts. Finally we discuss interesting patterns in our promising results, and future work to investigate the robustness of passthoughts in day-to-day life.

@@

The concept of in-ear EEG was introduced in 2011 with a demonstration of the feasibility of recording brainwave signals from within the ear canal \cite{Looney2011}. The in-ear placement can produce signal-to-noise ratios comparable to those from conventional EEG electrode placements, is robust to common sources of artifacts, and can be used in a brain-computer interface (BCI) system based on auditory and visual evoked potentials \cite{Kidmose2013a}. One study attempted to demonstrate user authentication using in-ear EEG, but was only able to attain an accuracy level of 80\%, limited by their use of a consumer-grade device with a generic fit, single-electrode earpiece \cite{curran2016passthoughts}. Our study improves on these results by incorporating a physical token (a possession factor) in the form of custom-fitted earpieces with three electrodes each vs. the single channel used in previous work. Furthemore, we use the OpenBCI system which allows us to capture raw data (the device used in previous work used an unknown proprietary algorithm), simultaneously record from the scalp for validation, and report impedance measures important to data quality and authentiation assessment.

@@

When proposing or evaluating authentication paradigms robustness against imposters is often the first consideration, but the usability of these systems is of equal importance as they must conform to a person's needs and lifestyle to warrant adoption and prolonged use. The authors of \cite{sasse2001} describe usability issues with knowledge-based systems like alphanumeric passwords, in particular that it should not be the burden of the user to remember complex passwords that have to be frequently changed. In \cite{braz2006}, researchers analyzed some of the complexities applying interface human factors heuristics to authentication, and indicate the importance of social acceptibility, learnability, and simplicity of authentication methods. Technology worn on the head faces particular usability issues; in their analysis of user perceptions of such devices, the authors of \cite{Genaro2014} identified design, usability, ease of use, and obtrusiveness among the top 10 concerns of users' online postings, and qualitatively comments around comfort and "looking weird".

In the proposed system we seek to incorporate the perspectives of this research. Passthoughts such as relaxed breathing or imagining favorite song are easy for a user to remember and perform, and the earpiece form factor of our system is intended to address wearability and social perception concerns.

@@

\begin{figure}[t]
\centering
\includegraphics[width=.75\linewidth]{./figures/CFEEEG_piecefig_Right.jpg}
\caption{Labeled photo of one of our manufactured custom-fit earpieces with thre embedded electrodes located in the concha, front-facing (anterior) in the ear canal, and back-facing (posterior) in the ear canal.}
\label{fig:earpiece_diagram}
\end{figure}

To produce custom ear impressions we first cleaned subjects' ears, placed a cotton ball with a string attached into the ear canal, and injected silicon into the canals. When the silicon dried after a few minutes, the string was pulled to remove the impression from the ear canal. This impression was then scanned with a 3D scanner and the resulting scan modified based on some heuristics to achieve a comfortable fit and to ensure the intended electrode sites will make good contact with the skin. Channels were created in the 3D model to allow wire leads and associated EEG electrodes as well as a plastic tube to deliver audio. This 3D model was then sent to a 3D printer after which wires, leads, and associated AgCl electrodes were installed. The positions of the earpiece electrodes were simplified from those described in \cite{Mikkelsen2015}. We reduced the number of canal electrodes in order to prevent electrical bridging and positioned them approximately 180 degrees apart in the canal (posterior/back and anterior/front locations in the canal). One other electrode was placed in the concha. An example of one of the manufactured earpieces is shown in Figure \ref{fig:earpiece_diagram}.

@@

We selected a set of mental tasks based on findings in related work regarding the relative strengths of different tasks in authentication accuracy and usability as reported by participants. \cite{Chuang2013b, curran2016passthoughts} Furthermore, given the in-ear placement of the electrodes and therefore the proximity to the temporal lobes containing the auditory cortex, we tested several novel authentication tasks based specifically on aural imagery or stimuli. The nine authentication tasks and their attributes are listed in Table \ref{tab:tasks}. Our strategy was to select tasks that captured a diversity across dimensions of external stimuli, involving a personal secret, eyes open or closed (due to known effects on EEG), and different types of mental imagery.

@@

\textbf{Task} & \textbf{Description} & \textbf{Stimuli}? & \textbf{Secret}? & \textbf{Eyes} & \textbf{Imagery}\\
\hline
Breathe & Relaxed breathing with eyes closed & No & No & Closed & None\\
Breathe - Open & Relaxed breathing with eyes open & No & No & Open & None\\
Sport & Imagine attempting a chosen physical activity & No & Yes & Closed & Motor\\
Song & Imagine hearing a song & No & Yes & Closed & Aural\\
Song - Open & Song task, with eyes open & No & Yes & Open & Aural\\
Speech & Imagine a chosen spoken phrase & No & Yes & Closed & Aural\\
Listen & Listen to noise modulated at 40 Hz & Yes & No & Closed & None\\
Face & Imagine a chosen person's face & No & Yes & Closed & Visual\\
Sequence & Imagine a chosen face, number, and word on timed cues & Yes & Yes & Open & Visual\\
\hline
\end{tabularx}
\caption{The nine authentication tasks and their properties. We selected tasks with a variety of different properties, but preferred tasks that did not require external stimuli, as the need to present such stimuli at authentication time could present challenges for usability and user security.}
\label{tab:tasks}%
\end{table*}

\subsection{Data Collection Protocol}
%\label{sec:org2041857}
All sites were cleaned with ethanol prior to electrode placement and a small amount of conductive gel was used on each electrode. For EEG recording we used an 8-channel OpenBCI system \cite{michalska2009openbci} which is open-source and costs about 600 USD; an alternative to medical-grade EEG systems (which cost \textgreater20,000 USD), with demonstrated effectiveness \cite{Frey2016}. The ground was placed at the center of the forehead, approximately AFz according to the 10-20 International Standard for Electrode Placement (ISEP), and reference on the left mastoid. The AFz ground location was intentional to not bias left or right ear recordings, though future systems using one ear only should test relocating the ground to a site on one ear (e.g. the earlobe). Six channels were used for the three electrodes on each earpiece (shown in Figure \ref{fig:earpiece_diagram}); for the remaining two channels one AgCl ring electrode was placed on the right mastoid for later re-referencing, and one at approximately Fp1 (ISEP location above the left eye) to validate the data collected in the ears against a common scalp-based placement. Before beginning the experiment, the data from each channel was visually inspected using the OpenBCI interface. Audio stimuli were delivered through small tubes in the earpieces.

During the experiment, participants were seated in a comfortable position in a quiet room facing a laptop on which the instructions and stimuli were presented using PsychoPy \cite{peirce2007psychopy}. All tasks were performed for five trials each, followed by another set of five trials each to reduce boredom and repetition effects. Each trial was 10 seconds in length, for a total of 10 trials or 100 seconds of data collected per task. The instructions were read aloud to participants by the experimenter, and participants advanced using a pointer held in their lap to minimize motion artifacts in the data. The experimenter also recorded the participant's chosen secrets for the \textit{sport}, \textit{song}, \textit{face}, \textit{speech}, and \textit{sequence} tasks and reminded the participant of these for the second set of trials. After EEG data collection, participants completed a usability questionnaire.

@@

It is important that the electrical impedances achieved for electrodes are low ($<$10 kOhm) to obtain quality EEG signals. Table \ref{tab:impedances} below summarizes the impedances across the seven participants' six ear channels. With the exception of a few channels in select participants, impedances achieved were good overall. Most of the recorded impedances of the earpiece electrodes were less than 5 k\(\Omega\), a benchmark used widely in previous ear EEG work, and all except two were less than 10 k\(\Omega\). Nonetheless, the data from all electrodes were tested in our other data quality test.

@@

Since past work has shown that classification tasks in EEG-based brain-computer interfaces (BCI) are linear \cite{Garrett2003a}, we used XGBoost, a popular tool for logistic linear classification \cite{Chen2016}, to analyze the mental task EEG data. Compared to other linear classifiers, XGBoost uses gradient boosting in which an algorithm generates aa decision tree of weak linear classifiers that minimizes a given loss function. Gradient boosting generally improves linear classification results without manually tuning hyperparameters.

@@

For the predictions, the evaluation regards the instances with prediction value larger than 0.5 as positive instances, and the others as negative instances. After updating classifier parameters, the classifier was tested on the withheld validation set. Since negative examples far outweigh positive examples in this dataset, XGBoost atuomatically optimized using the ”error” hyperparameter. Over a set of \(E\) examples containing \(E_W\) wrong examples \(E_W\subset{E}\), XGBoost's binary classification error rate \(\epsilon\) is calculated as

@@

To further test the robustness of the system, we also conducted a ”leave one out” process for the best performing tasks in which each participant’s FAR was calculated once with each other participant left out (e.g. CV for P1 with P2 left out, then CV for P1 with P3 left out, etc. for every participant combination).

@@

Our results indicate acceptable accuracy using data from the left ear alone. This corresponds to a desirable scenario, in which the device could be worn as a single earbud. As such, we focus on results from only the left ear in the following analyses.

@@

FAR and FRR results by task are shown in Figure \ref{fig:meanByTask}, averaged across participants. Across all tasks, the sport task produced the lowest FAR. Specifically, it produced 0.0\% FAR for all seven participants, with a corresponding 1.8\% FRR. This suggests that the authentication scheme can work very well even if we limit the passthoughts to just a single task category, where the users could choose a personalized secret for that task. Interestingly, tasks like \textit{breathe} and \textit{breathe - open} performed very well despite lacking a personalized secret, indicating that even when the task may be the same across participants our classifier was still able to distinguish between them.

@@

In addition to the scales and rankings, we included a few open response questions to ascertain attitudes around use cases for in-ear EEG and passthoughts, and the comfort of wearing an in-ear EEG device in everyday life. Participants first read the prompt, "Imagine a commercially available wireless earbud product is now available based on this technology that you've just experienced. It requires minimal effort for you to put on and wear.", and were asked about use cases for in-ear EEG and passthoughts. Responses about in-ear EEG expectedly included authentication for unlocking a phone or computer and building access, but also aspects of self-improvement such as P4's response "Help people increase focus and productivity". P5 and P6 also indicated a use for measuring engagement with media like movies and music, and relatedly P4 wrote "music playback optimized for current mental state and feelings". In terms of comfort wearing such a device, participants generally responded they would be comfortable, though P5 and P6 stipulated only when they already would be wearing something in the ears like earphones. Notably, three participants also added that imaginging a face was difficult and had concerns regarding their ability to repeat tasks in the same exact way each time.

A final component of usability we acquired was the ability of the participants to recall their specific chosen passthoughts. Participants were contacted via e-mail approximately two weeks after data collection and asked to reply with the passthoughts they chose for the \textit{song}, \textit{sport}, \textit{speech}, \textit{face}, and \textit{sequence} tasks. All participants correctly recalled all chosen passthoughts, with the exception of one participant who did not recall their chosen word component for the \textit{sequence} task.

@@

The real-world implications of this study are limited by the small, relatively homogeneous sample of participants. In the case of this initial evaluation however, the homogeneity of our participant pool can be seen as a strength of the reported results given that system is meant to distinguish between individuals. In order to establish the validity of this system for widespread real-world use we feel it is necessary to expand the size and diversity of participants in future studies. This sample size is comparable to that of other EEG passthoughts work \cite{Ashby2011, Marcel2007a, Poulos2002, Chuang2013b, curran2016passthoughts} and other custom-fit in-ear EEG research \cite{Kidmose2013a, Mikkelsen2015}. The fitting and manufacturing of custom-fit earpieces was the main limitation to increasing our sample size. This may very well pose a limitation in proliferation and adoption of such a technology as well, although recently there have been developments in at-home kits for creating one's own custom-fitted earpieces \cite{voix2015settable} that could help overcome this barrier.
